### 2015-06-26 reports/paper/system.tex
add

The end system has two arrays, each with three microphones mounted on the vertices of a $20$ cm equilateral triangle. We used omni-directional foil electret condenser microphone due to its low cost and small size. The microphone has a frequency range of $100$ to $10K$ Hz, and a minimum SNR of 58dB\cite{sys:1}. We also used operational amplifer OPA344 from Texas Instrument to amplify the microphone output by a factor of 100, so the received signal can be easily picked up by the analog-to-digital converter (ADC) module installed on the micro-controller. The micro-controller board used in this project is \emph{teensy 3.1}, and it is attached to one of the vertices of the triangle. Fig~\ref{fig:setup_array} shows a picture of the array setup.  The micro-controller contains an onboard RAM of $64$k, and an ADC module capable of sampling at $500$kHz~\cite{tdoa:micloc, sys:teensy}. In this project, the micro-controller collects microphone data on all three channels for a duration $12$ milliseconds and then sends the recorded data to a computer through the USB port for localization.

@@

>>>>

\subsection{Hardware}
The end system has two arrays, each with three microphones mounted on the vertices of a $20$ cm equilateral triangle. We used omni-directional foil electret condenser microphone due to its low cost and small size. The microphone has a frequency range of $100$ to $10K$ Hz, and a minimum SNR of 58dB\cite{sys:1}. We also used operational amplifer OPA344 from Texas Instrument to amplify the microphone output by a factor of 100, so the received signal can be easily picked up by the analog-to-digital converter (ADC) module installed on the micro-controller. The micro-controller board used in this project is \emph{teensy 3.1}, and it is attached to one of the vertices of the triangle. Fig~\ref{fig:setup_array} shows a picture of the array setup.  The micro-controller contains an onboard RAM of $64$k, and an ADC module capable of sampling at $500$kHz~\cite{tdoa:micloc, sys:teensy}. In this project, the micro-controller collects microphone data on all three channels for a duration $12$ milliseconds and then sends the recorded data to a computer through the USB port for localization.

@@

\subsection{Software}

On the software side, \emph{Python} is used as the main programming language since it has extensive libraries in both real time data handling and signal processing. \emph{zeroMQ} is an inter process messaging queue that is used in our system to pass data across different modules. Our system is made up of two data acquisition modules (each is used to receive raw date from microphone array output) and one localization module (listens to both data acquisition modules and perform localization using the raw microphone data). Using \emph{zeroMQ} as connections to different modules adds flexibility to our system, as we can design applications such as the drawing application we have used in our system to interface only with the localization module and disregard how the microphone data is collected. Other localization applications can be easily integrated into our system by connecting them with the localization module. Furthermore, we have built a recording module that interfaces with the data acquisition modules for offline analysis and parameter tuning.
